Negative Selection in the 20th Century

### 2020-10-07 why-negative-selection.Rmd
Changes to get drake working again after reinstating files

---
title: "Negative Selection in the 20th Century"
author: "David Hugh-Jones, Abdel Abdellaoui"
date: "April 2020"
bibliography: "negative-selection.bib"
output: 
  bookdown::pdf_document2:
    toc: false
    latex_engine: xelatex
---

>>>>

---
title: "Negative Selection in the 20th Century"
author: "David Hugh-Jones, Abdel Abdellaoui"
date: "July 2020"
bibliography: "negative-selection.bib"
output: 
  bookdown::pdf_document2:
    toc: false
    latex_engine: xelatex
---
